---
title: "HW4-Lin-Zhai"
author: "Lin Zhai"
date: "4/15/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

_1. Create a data frame in R based on this table and plot the data points with distance on the y-axis._

```{r}
h = c(1000, 800, 600, 450, 300, 200, 100)
d = c(573, 534, 495, 451, 395, 337, 353)
plot(h, d)
```


_2. Galileo believed there was a quadratic relationship between initial height and the distance traveled._

_* Fit an order 2 polynomial in height, with distance as the response._
```{r}
galileo.order2 <-lm(d~h+h^2)
summary(galileo.order2)

```


_* Fit a cubic (order 3) and a quartic (order 4) model for these data. What do they tell you about the nature of the relationship?_


```{r}
galileo.order3 <-lm(d~h +h^2 + h^3)
summary(galileo.order3)
galileo.order4 <-lm(d~h +h^2 + h^3 + h^4)
summary(galileo.order4)
```

Answer: Basically, it shows distance is significantly related to the initial height. However, the quarantic, cubit and quartic fits all seem reasonably good.

_3. Based on your models from (b), choose the one that you think best represents the data and plot the fitted line on the raw data. Add 90 percent confidence bands for mean distance traveled to the plot._

Answer: All the metircs of the three models are of the same values respectively. I would choose the order2 $$lm(formula = d ~ h + h^2)$$ to represent my model. 

```{r}
xseq <- data.frame(d,h)
ci.band <- predict(galileo.order2, newdata = xseq, interval = "confidence", level = 0.90)

```



_Install the package faraway and choose the data set trees, which provides data on the dimensions of felled trees of a certain type (see, for example, Atkinson, 1985)._

_1. Access the data object at the prompt and plot volume against girth (the latter along the x-axis)._

_2. Fit two models with Volume as the response: one quadratic model in Girth and the other based on log transformations of both Volume and Girth._


_3. Comment on the similarity (or difference) of the fits in terms of the coefficient of determination._

_4. Use predict to add lines to the plot from (d) for each of the two models from (e). Use different line types; add a corresponding legend. Also include 95 percent prediction intervals, with line types matching those of the fitted values (note that for the model that involves log transformation of the response and the predictor, any returned values from predict will themselves be on the log scale; you have to back-transform these to the original scale using exp before the lines for that model can be superimposed). Observe respective fits and their estimated prediction intervals._

_Lastly, turn your attention back to the mtcars data frame. 1. Fit and summarize a multiple linear regression model to determine mean MPG from horsepower, weight, and displacement. 1. Use I to refit the model in (g) in terms of GPM = 1/ MPG. Which model explains a greater amount of variation in the response?_



## Including Plots



```{r pressure, echo=FALSE}
plot(pressure)
```


